Sample MICS Paper Title

### 2014-03-13 paper/tex/Paper.tex
typo

%continue assignment
The node in the frontier with the lowest cost is removed from the frontier and used to generate child nodes. To generate a child node, a tile is added to the end of the node. A child node is generated for all unplaced tiles that are either in the place holder group or in the group matching the corresponding amino acid in the protein chain. A cost of placing the tile is then generated. The cost is a sum of the cost of placing the previous tiles in the node, how well the tile matched the corresponding amino acid in the protein chain and how well the tile's residue $i-1$ values match the residue $i$ values of the tile placed before it. The child nodes are then added to the frontier, and the process of generating child nodes is repeated.

>>>>

%continue assignment
The node in the frontier with the lowest cost is removed from the frontier and used to generate child nodes. To generate a child node, a tile is added to the end of the node. A child node is generated for all unplaced tiles that are either in the place holder group or in the group matching the corresponding amino acid in the protein chain. A cost of placing the tile is then generated. The cost is a sum of the cost of placing the previous tiles in the node, how well the current tile matched the corresponding amino acid in the protein chain and how well the tile's residue $i-1$ values match the residue $i$ values of the tile placed before it. The child nodes are then added to the frontier, and the process of generating child nodes is repeated.
